\section{Graphical User Interface}
\label{sec:graphical_user_interface}

The Student and Admin users will interact with a graphical user interface to
take and run the quiz. The model deals with the data so the GUI can just be a
visual interaction and representation of the client model. Instead of having
many pop ups for each of the GUI panels, we decided to have one frame per
client in which its content panel changes depending on the current part of the
quiz.

\begin{enumerate}

	\item \textbf{Model/View Seperation}

		Originally we decided that the GUI would follow a model/view separation
		format where the model will be separate from the client. This, however,
		caused some problems so we decided to not have a separate model and use
		the client as the model instead. One of the problems we encountered was
		that the GUI would interact with the model and create an object that
		needs to be sent to the server. We found it tricky to find a way to
		send objects from the model to the client and realized that there was a
		lot of redundancy as objects had to go through the model and the client
		when really there only needed to be one.

	\item \textbf{GUI Panels}

		Each GUI panel used in the quiz has its own class.  When a client is
		created, each of the GUI panels is instantiated and added to an array.
		To accomplish this we used inheritance. Each of the GUI panels extends
		the abstract class \texttt{MasterFrame}, and in turn,
		\texttt{MasterFrame} extends \texttt{JPanel}.  Each of the GUI panels
		is added to the \texttt{guiElements}' \texttt{MasterFrame[]}.
		\texttt{MasterFrame} is an abstract class with one abstract method
		\verb+resetDisplay()+.  This method is used to reset the contents of
		the current panel to an updated version of the model.  Whenever the
		content panel of the frame is changed, the \verb+resetDisplay()+ method
		is called to ensure correct information is displayed.

		The overall GUI will display different panels depending on which part of
		the system is currently being used. The GUI panels are:

	\begin{description}

		\item[\texttt{LoginFrame}]\hfill \\ The first panel users will log-in
			to (both Admin and Student). \texttt{LoginFrame} contains a
			username field, a password field and login button. When the login
			button is activated, it send the contents of the two fields to the
			client model to create a \texttt{LoginRequest} object using the
			\verb+requestLogin()+ method.

		\item[\texttt{StudentHomeFrame}]\hfill \\ The panel a Student will see
			once they have logged in / received successful login reply object.
			Here they can push the Start quiz button which adds them to a pool
			of Students ready to start the quiz. This leads them to the
			\texttt{WaitingFrame} panel using the
			\verb+requestWaitingScreen()+ method.

		\item[\texttt{AdminHomeFrame}]\hfill \\ The panel the Admin will see
			once they have logged in / received successful login reply object.
			Here they can see which Students have connected and joined the
			waiting pool to start the quiz. \texttt{AdminHomeFrame} has a
			\texttt{JComboBox} which lists the possible quizzes to run. This
			uses the \verb+setCurrentQuizID()+ method. The Admin can then
			push the start quiz button which sends the selected quiz to all the
			waiting Students using the \verb+adminStart()+ method.

		\item[\texttt{WaitingFrame}]\hfill \\ The panel a Student will see when
			they have pushed start and are waiting for the Admin to start
			the quiz. Contains a message to the Student letting them know
			they are waiting for the Admin to start the quiz as well as a
			JProgressBar in intermediate state.

		\item[\texttt{QuestionFrame}]\hfill \\ The panel which displays the
			question to the Students. This panel is Is only displayed for a
			limited time as each question has a short time limit. The question
			is displayed in a \texttt{JTextPane,} and each of the four possible
			multiple choice answers is displayed as a \texttt{JButton} beneath.
			To the side there is a countdown timer which visually displays the
			time to answer the question. As soon as the question is answered or
			the time has run out, the panel is changed to the
			\texttt{StudentResultsFrame} panel. When a button is pushed, the
			\verb+setResponseNumber(i)+ method is called. If a Student
			doesn't answer, then the response number is set to -1.

		\item[\texttt{StudentResultsFrame}]\hfill \\ Once a Student has
			completed a question, they are displayed with this panel.
			\texttt{StudentResultsFrame} displays the last question with
			highlighted text for the correct answer and Students answer. It
			also displays the score received for the last question and current
			leader board for the quiz where each client is ranked by their
			total score so far. This panel is shown for a set amount of time
			before leading back to the \texttt{QuestionFrame} for a new
			question.

		\item[\texttt{AdminResultsFrame}]\hfill \\ The
			\texttt{AdminResultsFrame} is displayed once the Admin has started
			the quiz. It displays the current question Students are completing
			and a live leader board showing the current scores of the Students.
			The leader board ranks the Students by their current total score
			from the completed questions so far.

		\item[\texttt{FinalResultsFrame}]\hfill \\ This is similar to
			\texttt{StudentResultsFrame} but is the final panel the Student
			sees in the quiz. It shows the correct answers to the previous
			question and the score for the previous question. It also shows the
			final leader board rankings. Unlike \texttt{StudentResultsFrame,}
			there is no time limit so the Student can see the final results as
			long as they wish. There is a back button to return the Student to
			the \texttt{StudentHomeFrame} which uses the \verb+returnHome()+
			method.

	\end{description}

	Other GUI components that we have created and used within the GUI panels are:

	\begin{description}

		\item[\texttt{CountDownTimer}]\hfill \\ \texttt{CountDownTimer} is GUI
			component that counts down seconds. It shows a
			\texttt{JProgressBar} decrease as the time decreases. Also has a
			label beneath showing the seconds left to count down. Used in
			\texttt{QuestionFrame}.

		\item[\texttt{LeaderBoard}]\hfill \\ A table consisting of each Student
			in the quiz, their position and score. This is updated whenever the
			\verb+resetDislplay()+ method is called in its parent panel
			(\texttt{MasterFrame}). Used in \texttt{StudentResultsFrame,}
			\texttt{AdminResultsFrame} and \texttt{FinalResultsFrame}.

	\end{description}

\end{enumerate}
