\tablepage%
\begin{landscape}

\section{Test Plan}
\label{sec:test_plan}

\renewcommand{\arraystretch}{1.3}
\begin{longtabu}{c l X c c}
\toprule
S.No & Category & Description & Expected Result & Actual Result \\
\midrule
1 & Registration & User is able to register by providing first name, last name,
username and password. & & \\

2 & Registration & System should display username and password guidelines to
users. & & \\

3 & Registration & System validates the credentials; dispays an error message
if user provides invalid username and password and asks user to choose valid
credentials. & & \\

4 & Registration & If user enters valid credentials, system checks if the
entered credentials already exists in the the users table. If credentials
exists, system asks the user to choose different credentials. & & \\

5 & Registration & System inserts the credentials in the users table if the
user enters valid credentials. A unique ID is created for the user in users
table. & & \\

6 & Login & System displays the login page where user can enter username and
password and login to the system. & & \\

7 & Login & System checks the entered credentials in the users table; displays
an error message if incorrect credentials are entered and asks user to re-enter
credentials. & & \\

8 & Login & If correct credentials are entered, user is taken to the Home page.
& & \\

9 & HomePage-Student & Student homepage should display the buttons – Start,
View Result, Update Profile and Quiz rules. & & \\

10 & HomePage-Student & Quiz should start when student clicks on ``Start''
button. & & \\

11 & HomePage-Student & Quiz result should be displayed when student clicks on
``View Result'' button. What is shown in View Result page? & & \\

12 & HomePage-Student & Profile page should be displayed when student clicks on
``Update Profile'' button. User should be able to edit profile; save changes or
cancel changes. & & \\

13 & HomePage-Student & Quiz rules should be displayed when stuent clicks on
``Quiz Rules'' button. A new window or a popup screen? & & \\

14 & HomePage-Admin & Admin homepage should display the buttons – Start, View
Result, Question settings (Add, remove or update questions), Update Profile.
(Check the options displayed). & & \\

15 & HomePage-Admin & Admin should be able to select a quiz and click on Start
to start the quiz. & & \\

16 & HomePage-Admin & Quiz result should be displayed when admin clicks on
``View Result'' button. What is shown in View Result page? & & \\

17 & HomePage-Admin & Admin should be able to add, remove or update
questions/answers in questions table in the Question settings page. & & \\

18 & HomePage-Admin & Profile page should be displayed when admin clicks on
``Update Profile'' button. Admin should be able to edit profile; save changes or
cancel changes. & & \\

19 & Play Quiz-Student & The quiz name should be displayed in quiz page. & & \\

20 & Play Quiz-Student & Each quiz consists of 10 questions. & & \\

21 & Play Quiz-Student & Each question has a set of possible answers (maximum
4). & & \\

23 & Play Quiz-Student & Timer is displayed when question appears on screen. &
& \\

24 & Play Quiz-Student & Student is able to choose an answer by clicking on the
answer. & & \\

25 & Play Quiz-Student & When a student chooses the correct answer before time
runs out, timer stops. The other students should not be able to select an
option once the timer stops. & & \\

26 & Play Quiz-Student & After quiz finishes, the result is inserted into
user\_result table. & & \\

27 & Play Quiz-Student & Student should be able to see feedback after quiz
finishes. & & \\

28 & Play Quiz-Student & Student should be able to view result after quiz
finishes (and after answering a question?). & & \\

29 & Play Quiz-Student & Student should b able to view the historical result
data from user\_result table after quiz finishes. & & \\

30 & Play Quiz-Student & Student should be able to click on the close buttom to
exit the quiz. & & \\

31 & Play Quiz-Admin & Admin should be able to click on start button to start
the quiz once all students have logged in. & & \\

32 & Play Quiz-Admin & Admin should be able to see the result after each
question is answered. & & \\

33 & Play Quiz-Admin & Admin should be able to see the result summary after
quiz finishes. & & \\

34 & Play Quiz-Admin & Student should be able to click on the close buttom to
exit the quiz. & & \\

35 & Server-Client & System ensures that all clients and server are
synchronised. & & \\

36 & JDBC & Database connection is established from JDBC\@. & & \\
\bottomrule
\end{longtabu}
\end{landscape}
\restoregeometry%
